\part{Issues Encountered}
    \section{Guaranteed AI}
        For this AI, at the beginning we only made a few strategies, and after a while we had a lot of ideas and we wanted to make a lot of strategies. 
        Of course making many strategies took a long time, particularly in November.
        Also the more strategies appeared the more difficult it began to abstract them.
        
        After making a good amount of different strategies to fulfill our goal which was to compose with multiple strategies, it appeared that some of them were already really efficient against the Random AI. The difficulty that occurred when we began to compose our own AI was to make a better AI than our classic AI which used only one type of strategy. Making a lot of strategies was really long and for this stage we didn't have much time, but in the end we succeeded at making a better AI.
    
    \section{Ambitious AI}
        \subsection{Another type of Monte Carlo}
            When we were thinking about which kind of ambitious AI we wanted to implement, we had two different ideas of how to implement Monte Carlo.
            But after some time of reflection we decided that it was repetitive and not useful. It was more interesting to choose one, and look for something else.

        \subsection{Reinforcement Learning}
            Reinforcement learning is a type of AI which makes us dream and looks really interesting.
            When we started doing some researches about machine learning, we thought it would be perfect for Seasons. Classic machine learning would have required a huge amount of data which we couldn't have, thus making reinforcement learning a good alternative as it would learn on its own with each game.
            But when we actually tried to implement it, we quickly realized the game was not adapted for it, and we would have had to spent too much time trying to make it work.
            
            So as we were getting short on time, we decided to simply improve already existing strategies until we'd find something good.
        
            
            
    